An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-08-01 VLDB2026/main.tex
Update main.tex

	\begin{definition}[AF-NN Search]
		Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute set \( s_i \). Given a query \( Q = (q_v, q_s, k) \), where \( q_s \) is the query attribute set, the AF-NN search aims to return a set \( R \subseteq D_s \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_s \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_s = \{ v_i \mid (v_i, s_i) \in D \land q_s \subseteq s_i \} \).
	\end{definition}

@@

		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \). Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).
	\end{definition}

>>>>

	\begin{definition}[AF-NN Search]
		Let \( D = \{(v_1, s_1), \ldots, (v_n, s_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, where each \( v_i \) associated with an attribute set \( s_i \). Given a query \( Q = (q_v, q_s, k) \), where \( q_s \) is the query attribute set, the AF-NN search aims to return a set \( R \subseteq D_s \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_s \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_s = \{ v_i \mid (v_i, s_i) \in D \land q_s \subseteq s_i \} \).
	\end{definition}

@@

		Let \( D = \{(v_1, \textcolor{blue}{a}_1), \ldots, (v_n, \textcolor{blue}{a}_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, where each \( v_i \) associated with an attribute value \( a_i \). Given a query \( Q = (q_v, [a_{\min}, a_{\max}], k) \), where \( a_{\min} \) and \( a_{\max} \) denote the lower and upper bounds of the query range, respectively, the RF-NN search aims to return a set \( R \subseteq D_a \) with \( |R| = k \), such that for any \( x \in R \) and \( y \in D_a \setminus R \), \( \textit{dist}(q_v, x) \leq \textit{dist}(q_v, y) \), where \( D_a = \{ v_i \mid (v_i, a_i) \in D \land a_{\min} \leq a_i \leq a_{\max} \} \).
	\end{definition}
